Familial consequences of the Covid-19 in Québec: Comparison between immigrants and natives

### 2023-05-02 Codes/Trajipaq_covid_an1.Rmd
Revert "Trajipaq_covid_an1.Rmd"
J'ai restauré le fichier Trajipaq_covid_an1.Rmd sur lequel j'avais expérimenté hier soir.

library(tidyverse)
library(summarytools)
library(srvyr)
library(survey)
library(ggpubr)
library(writexl)
library(haven)

Base_Trajipaq_Finale_Ok <- read_dta("~/GitHub/Projet_Immigration_Trajipaq/Data/Base_Trajipaq_Finale_Ok.dta")

>>>>

library(tidyverse)
library(summarytools)
library(srvyr)
library(survey)
library(ggpubr)
library(writexl)

trajipaq_covid <- read_rds("../Data/trajipaq_covid.RData")
